{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-12 paper/paper.tex
first part of syntax and semantic

\subsection{Syntax and Semantics of multithreaded programs}
\label{sec:syntaxsemantics}
\subsection{Type system}
\label{sec:typesystem}
\subsection{Soundness}
\label{sec:soundness}
\subsection{Instantiation}
\label{sec:instantiation}

>>>>

\subsection{Syntax and Semantics of multithreaded programs}
\label{sec:syntaxsemantics}
A program is viewed as an abstract thing, which consists of a set of
program points $\mathcal{P}$ with a distinguished entry ($1$) and exit
(\texttt{exit}) point and a function that maps program points to
instructions.

These instructions are not further specified, but contain an instruction
to start a new thread (\texttt{start \textit{pc}} where pc is the start
instruction of the new thread).

Further there is a relation $\mapsto$ that describes possible successor
instructions. \texttt{exit} is the only instructions with no successor
and \texttt{start \textit{pc}} may only have a single successor (the
following program point).

\subsection{Type system}
\label{sec:typesystem}
\subsection{Soundness}
\label{sec:soundness}
\subsection{Instantiation}
\label{sec:instantiation}
